Fast Sorting on Modern Computers

### 2005-08-13 docs/tech_report/merge.tex
fixed up the graphs, involving changes to code, gnuplot scripts, tex files and the README

\sixplot{algorithm_n_0.eps}{algorithm_s_0.eps}{base_mergesort_0.eps}{double_aligned_tiled_mergesort_0.eps}{double_aligned_multi_mergesort_0.eps}{double_aligned_multi_mergesort_0.eps}{mergesorts}

>>>>

\sixplot{algorithm_n_0.eps}{algorithm_s_0.eps}{base_mergesort_0.eps}{double_aligned_tiled_mergesort_0.eps}{double_aligned_multi_mergesort_0.eps}{double_aligned_multi_mergesort_1.eps}{mergesorts}

### 2005-08-13 docs/tech_report/quick.tex
fixed up the graphs, involving changes to code, gnuplot scripts, tex files and the README

% \sixplot{base_quicksort_0.eps}{base_quicksort9_0.eps}{cache_quicksort_0.eps}{multi_quicksort_0.eps}{sequential_multi_quicksort_0.eps}{}{base, cache and multi quicksorts and base quicksort9}

\sixplot{base_quicksort__median_of_3__0.eps}{memory_tuned_quicksort_0.eps}{multi_quicksort__binary_search__0.eps}{multi_quicksort__sequential_search__0.eps}{}{}{base,
memory-tuned and multi quicksorts}

>>>>

\sixplot{base_quicksort__median_of_3__0.eps}{memory_tuned_quicksort_0.eps}{multi_quicksort__binary_search__0.eps}{multi_quicksort__sequential_search__0.eps}{}{}{base,
memory-tuned and multi- quicksorts}
